The Local Group in the Cosmic Web

### 2014-10-20 paper/main.tex
re-escribiendo la discusion sobre alineacion

These alignments for the LG pairs could be in contradiction with
some findings
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
that report a universal trend where the eigenvector $\hat{e}_{3}$
(i.e. the filament direction) marks the infall direction for
substructures. The Milky Way satellites are located at high
galactic latitudes, almost perpendicular to the vector pointing
towards the Andromeda Galaxy, which is the direction that we found aligned with
$\hat{e}_3$.

>>>>

How can we related these alignments to the observed LG? 
To evaluate this point we use observational information for the
satellite distribution around the LG galaxies.  The MW satellites are
located at high galactic latitudes forming a planar structure that
forms an angle of $42^{\circ}-52^{\circ}$, $\mu=0.6-0.7$ with the
vector joining the MW and M31; while the M31 satellites are on a plane
that lies on the same vector. \citep{Pawloski2013,Shaya2013}.

Most $\Lambda$CDM studies find that sub-structure infall direction is
done along $\hat{e}_{3}$ (the direction of filaments)
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}. The
alignment
